\input{cvstyle.tex}

\title{Frédéric Moser \\ {\small \href{http://fxi.io}{\tt http://fxi.io}}}
\begin{document}
\maketitle

% --------------{ Contact info}--------------- %

{\small
  \faPencil \hspace{0.2em} \href{mailto:f@fxi.io?Subject=job}{\tt f@fxi.io}\hfill
    \faGithub \hspace{0.2em} \href{https://github.com/fxi}{\tt github.com/fxi}\hfill
    \faPhone \hspace{0.2em} {\tt +41(0)77-411-27-04 \hfill}
  \faHome \hspace{0.2em} {\tt 5, Chemin de la Gravière -- CH-1225 \textsc{Chêne-Bourg}}
}

\begin{multicols}{2}

% --------------{ Objectif de carrière }--------------- %

\section*{Career objective}
Aspire to join an innovative, eco-conscious organization to contribute through advanced problem-solving skills and technical expertise, driving sustainable solutions.

\section*{Work experience}
\begin{cvPrint}
% --------------{ unep / who }--------------- %

\cvEntry{06/2015 -- present}{Lead Developer}{University of Geneva  (80\%)}{Geneva}{%
    Development of \texttt{MapX}, a platform for mapping and visualizing specialized scientific data.
    \begin{itemize}
      \item Developed the initial prototype using Shiny in two weeks.
      \item Migrated critical parts to a Dockerized stack using \texttt{Node.js}, \texttt{PostgreSQL}, \texttt{Redis}, \texttt{Traefik},  \texttt{MeilliSearch}, and a \texttt{JavaScript} single-page application frontend.
      \item Implemented key features including multi-source join editor, real-time attribute table editor using \texttt{WebSocket}, print-quality map export, story-map engine, \texttt{GeoServer} bridge for \texttt{OGC} standards, statistical tools, \texttt{SDK} integration package, and project management for users and vector geospatial data.
      \item Improvement of the platform to support thousands of users from all \textsc{un} countries.
    \end{itemize}
    \url{https://mapx.org}
}

\cvEntry{11/2014 -- present}{Lead Developer}{University of Geneva (20\%)}{Geneva}{%
  Development of \texttt{AccessMod~5}, a \textsc{who}-supported desktop application for anisotropic accessibility analysis and modeling.
  \begin{itemize}
    \item Developed a full-featured, user-friendly, and free replacement for \texttt{AccessMod~4} in 6 months using only open-source tools.
    \item Provided long-term support for the platform by integrating new features and ensuring maintenance, performance improvements while migrating towards a Docker-centric multi-architecture platform and an \texttt{Electron} based app manager.
    \item Achieved \texttt{AccessMod~5} recognition as a Digital Public Good.
  \end{itemize}
  \url{https://www.accessmod.org}
}
\cvEntry{08/2013 -- 06/2014}{Research Assistant}{University of Geneva}{Geneva}{%
  Contributed to multiple projects focusing on biodiversity and geomatics. Key achievements:
  \begin{itemize}
    \item Conducted map/reduce operations on multi-terabyte text files and analyzed a stochastic water flow model for the \textsc{acqwa} project.
    \item Developed \texttt{lebamod}, an interactive web application using \textsc{hpc} for configuring, fitting, and analyzing neural network models.
    \item Automated statistical predictions of discharge for multiple hydrological stations using \texttt{R} scripts.
    \item Enhanced \texttt{hexdim}, a web application for spatial exploration of species distribution predictive models.
    \item Transitioned ArcGIS workshops to open-source GIS solutions and contributed to introductory geomatics courses.
  \end{itemize}
}
\end{cvPrint}

\section*{Education}
\begin{cvPrint}
\cvEntry{2010 -- 2013}{Master of Environmental Sciences}{University of Geneva}{Genève}{%
  Thesis : \textsl{Impact of climatic changes on alpine biodiversity: species distribution modeling for aquatic insects in the Rhône watershed in Valais.} \\
  {\footnotesize Direction : D\up{r} E. Castella \& Prof. D\up{r} A. Lehmann. }
}
\cvEntry{2007 -- 2010}{Bachelor of Arts in Geography}{University of Geneva}{Genève}{%
  Thesis : \textsl{Shared space concept as a solution to reconsider street design on a human scale}\\
  {\footnotesize Direction : D\up{r} B. Levy.}
}
\end{cvPrint}


% --------------{ Skills }--------------- %

\section*{Computer Skills}
\footnotesize{Scale: \score{1}{5} = basic, \score{5}{5} = advanced}
\begin{multicols}{2}
\setlength{\columnseprule}{0.0pt}



\subsection*{Programming Languages}
\noindent\begin{tabular}{ll}
\score{4}{5} & \texttt{JavaScript} \\
\score{4}{5} & \texttt{R} \\
\score{4}{5} & \texttt{HTML5/CSS} \\
\score{3}{5} & \LaTeX \\
\score{3}{5} & \texttt{Shell Scripts} \\
\score{1}{5} & \texttt{C} \\
\end{tabular}

  \subsection*{Databases}
\noindent\begin{tabular}{ll}
\score{4}{5} & \texttt{PostgreSQL} \\
\score{2}{5} & \texttt{SQLite} \\
\end{tabular}

\subsection*{GIS Software}
\noindent\begin{tabular}{ll}
\score{4}{5} & \texttt{Grass GIS} \\
\score{4}{5} & \texttt{PostGIS} \\
\score{3}{5} & \texttt{QGIS} \\
\score{1}{5} & \texttt{ArcGIS} \\
\end{tabular}

\subsection*{Development tools}
\noindent\begin{tabular}{ll}
\score{4}{5} & \texttt{Shiny (R)} \\
\score{4}{5} & \texttt{Mapbox GL (JS)} \\
\score{4}{5} & \texttt{Webpack (JS)} \\
\score{4}{5} & \texttt{Docker} \\
\score{4}{5} & \texttt{vim} \\
\score{4}{5} & \texttt{git} \\
\score{3}{5} & \texttt{Caret (R)} \\
\score{3}{5} & \texttt{GDAL} \\
\score{3}{5} & \texttt{Electron} \\
\score{3}{5} & \texttt{Packer} \\
\end{tabular}




\subsection*{Operating Systems}
\noindent\begin{tabular}{ll}
\score{4}{5} & \texttt{MacOS} \\
\score{3}{5} & \texttt{Alpine Linux} \\
\score{2}{5} & \texttt{Ubuntu Server} \\

\end{tabular}

\end{multicols}

% --------------{ Langues }--------------- %

\section*{Language Proficiency}
\begin{itemize}
\item \textbf{\sffamily Français} : Native
\item \textbf{\sffamily English} : Intermediate
\item \textbf{\sffamily Deutsch} : Basic
\end{itemize}

% --------------{ Autres formation }--------------- %

\section*{Previous education}

\begin{cvPrint}
\cvEntry{2000 -- 2001}{Diploma of Watchmaker Rhabilleur}{School of Watchmaking}{Petit-Lancy}{%
Received a Fondation Hans-Wilsdorf prize for exceptional craftsmanship and skill.
}
\cvEntry{1997 -- 2000}{Diploma of Watchmaker Praticien}{Patek Philippe Geneva \& School of Watchmaking}{Plan-les-Ouates}{%
Completed intensive training in watchmaking, specializing in precision mechanics and fine adjustments.
}
\end{cvPrint}

\section*{Previous work experiences}
\begin{cvPrint}
\cvEntry{09/2009 -- 02/2014}{Computer Technician}{MacWorks SàRL (20-50\%)}{Geneva}{%
Performed computer and smartphone repairs, micro-welding, troubleshooting, and data recovery, with a focus on reducing environmental impact through repair and reuse.
}
\cvEntry{11/2001 -- 09/2010}{Watchmaker}{Self-employed, Andersen S.A. (20-100\%)}{Geneva}{%
Designed, prototyped, and produced horological complications with a focus on precision manufacturing processes. Developed awareness of the negative impact of the luxury industry on the world.
}
\cvEntry{12/2001 -- 06/2008}{Bicycle Messenger}{Krick Cyclomessagerie; dvdmania; Factotum (10-20\%)}{Geneva}{%
Handled express deliveries in urban areas, developing a strong commitment to social and environmental causes.
}

\vfill
\cvEntry{05/2005 -- 12/2008}{Civilian Service}{Genève Roule, \textsc{iaug}, Agricultural Operations}{Switzerland}{%
Chose civilian service as a conscientious objector, foregoing military duty. Engaged in diverse roles spanning technology, leadership, and manual labor, demonstrating adaptability and skill growth. Highlights include:
\begin{itemize}
\item Developed and implemented an efficient HR management application, for a non-profit public-benefit association.
\item Led teams across various settings, promoting teamwork and ensuring project completion.
\item Supported sustainable agriculture through hands-on involvement in agricultural operations, including maintenance, carpentry, and farming tasks.
\end{itemize}
}
\end{cvPrint}

% --------------{ Extra-professionnelles }--------------- %

\section*{Extracurricular activities}

\begin{cvPrint}

\cvEntry{04/2005 -- 04/2024}{Committee Member, Member}{Association Roue Libre}{Geneva}{%
  Actively promoted bicycle usage through cultural, sports, and various activities within the community. Highlights:
  \begin{itemize}
    \item Handled communication initiatives to enhance community engagement and increase association visibility.
    \item Designed and implemented software/hardware systems for interactive static bicycle races, boosting event participation.
    \item Coordinated over 100 volunteers for the Swiss Bicycle Messenger Championship 2005, leading to a successfully managed major event.
    \item Maintained and updated the association's website, improving user experience and information accessibility.
  \end{itemize}
}

\end{cvPrint}
\end{multicols}
\end{document}
